---
output:
  html_document: default
  pdf_document: default
---
```{r include = FALSE}
library(datasets)
flights = read.csv("flights.csv")
# Prototype to silence errors
sort_airports_by_delay = function(frame) {}
plot_flight_times = function(frame) {}
```

# Example Data
```{r}
head(flights)
```

# Data Scructure
## Columns
- origin - factor representing departure airport
- dep_delay - number of minutes delayed

# sort_airports_by_delay

## Description 
Returns data frame containing each origin airport and its average departure delay, sorted by delay in descending order.

## Parameters
1. frame - data frame containing columns described above

## Return Value 
Data frame containing each origin airport and its average departure delay, sorted by delay in descending order.

## Example
```{r error = TRUE, message = FALSE}
sorted = sort_airports_by_delay(flights)
```

# plot_flight_times

## Description 
Plot line graph of flight distance to flight time

## Parameters
1. frame - data frame containing columns described above

## Return Value 
none

## Example
```{r error = TRUE, message = FALSE}
unused = plot_flight_times(flights)
```

