---
output:
  html_document: default
  pdf_document: default
---
```{r include = FALSE}
library(datasets)
library(NYC2013FlightStats)
# Prototype to silence errors
# sort_airports_by_delay = function(frame) {}
# plot_flight_times = function(frame) {}
# flights_per_origin_chart = function(frame) {}
# destinations_sorted = function(frame) {}
```

# Example Data
```{r}
data("flights")
head(flights)
```

# Data Scructure
## Columns
- origin - factor representing departure airport
- dest - factor representing destination airport
- dep_delay - number of minutes delayed
- air_time - flight duration in air

# sort_airports_by_delay

## Description 
Returns data frame containing each origin airport and its average departure delay, sorted by delay in descending order.

## Parameters
1. frame - data frame containing columns described above

## Return Value 
Data frame containing each origin airport and its average departure delay, sorted by delay in descending order.

## Example
```{r}
sort_airports_by_delay(flights)
```

# plot_flight_times

## Description 
Plot line graph of flight distance to flight time

## Parameters
1. frame - data frame containing columns described above

## Return Value 
none

## Example
```{r}
plot_flight_times(flights)
```

# flights_per_origin_chart

## Description 
Plot pie chart of flight origins by frequency

## Parameters
1. frame - data frame containing columns described above

## Return Value 
none

## Example
```{r}
flights_per_origin_chart(flights)
```

# destinations_sorted

## Description 
sorts frequency of each destination airport into a data frame

## Parameters
1. frame - data frame containing columns described above

## Return Value 
data frame

## Example
```{r}
destinations_sorted(flights)
```
